GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-04-08 ms-swe-handbook.tex
updates

The MS in Software Engineering (MS-SWE) program prepares students to become leaders in engineering high quality, large scale, computing solutions to real life problems. The MS-SWE program prioritizes working professionals—as such, all SWE courses are taught \emph{late afternoon} or \emph{early evening}.

@@

Students are required to complete \textbf{30 credits} corresponding to \textbf{10 graduate courses}. Students are encouraged to download the course planner spreadsheet, and update it as they proceed through the program.

@@

\begin{enumerate}
    \item \textbf{SWE 619} Object-Oriented Software Specification and Construction
    \item \textbf{SWE 621} Software Modeling and Architectural Design
    \item \textbf{SWE 632} User Interface Design and Development
    \item \textbf{SWE 637} Software Testing
\end{enumerate}

@@

\begin{itemize}
    \item CS 540 Language Processors (Compilers)
    \item CS 550 Database Systems
    \item CS 555 Computer Communications and Networking
    \item CS 571 Operating Systems
    \item CS 584 Theory and Applications of Data Mining
    \item CS 675 Distributed Systems
    \item CS 678 Advanced Natural Language Processing
\end{itemize}

@@

\begin{itemize}
    \item ISA 562 Information Security Theory and Practice
    \item ISA 650 Security Policy
    \item ISA 673 Operating Systems Security
\end{itemize}

\item Information Systems (INFS)
\begin{itemize}
    \item INFS 740 Database Programming for the World Wide Web
\end{itemize}

\item Operations Research (OR)
\begin{itemize}
    \item OR 542 Operations Research: Stochastic Models
\end{itemize}

>>>>

% https://cs.gmu.edu/current-students/ms-students/ms-in-software-engineering/

The MS in Software Engineering (MS-SWE) program prepares students to become leaders in engineering high quality, large scale, computing solutions to real life problems. The MS-SWE program prioritizes working professionals--as such, all SWE courses are taught \textbf{late afternoon} or \textbf{early evening}.

@@

Students are required to complete \textbf{30 credits} corresponding to \textbf{10 graduate courses}. Students are encouraged to download the \href{https://cs.gmu.edu/media/uploads/programs/graduate/masters/ms-swe-courseplanner.xlsx}{course planner spreadsheet}, and update it as they proceed through the program.

@@

\begin{enumerate}
    \item \href{https://catalog.gmu.edu/search/?P=SWE%20619}{\textbf{SWE 619}} Object-Oriented Software Specification and Construction
    \item \href{https://catalog.gmu.edu/search/?P=SWE%20621}{\textbf{SWE 621}} Software Modeling and Architectural Design
    \item \href{https://catalog.gmu.edu/search/?P=SWE%20632}{\textbf{SWE 632}} User Interface Design and Development
    \item \href{https://catalog.gmu.edu/search/?P=SWE%20637}{\textbf{SWE 637}} Software Testing
\end{enumerate}

@@

\begin{itemize}
    \item \href{https://catalog.gmu.edu/search/?P=CS%20540}{CS 540} Language Processors (Compilers)
    \item \href{https://catalog.gmu.edu/search/?P=CS%20550}{CS 550} Database Systems
    \item \href{https://catalog.gmu.edu/search/?P=CS%20555}{CS 555} Computer Communications and Networking
    \item \href{https://catalog.gmu.edu/search/?P=CS%20571}{CS 571} Operating Systems
    \item \href{https://catalog.gmu.edu/search/?P=CS%20584}{CS 584} Theory and Applications of Data Mining
    \item \href{https://catalog.gmu.edu/search/?P=CS%20675}{CS 675} Distributed Systems
    \item \href{https://catalog.gmu.edu/search/?P=CS%20678}{CS 678} Advanced Natural Language Processing
\end{itemize}

@@

\begin{itemize}
    \item \href{https://catalog.gmu.edu/search/?P=ISA%20562}{ISA 562} Information Security Theory and Practice
    \item \href{https://catalog.gmu.edu/search/?P=ISA%20650}{ISA 650} Security Policy
    \item \href{https://catalog.gmu.edu/search/?P=ISA%20673}{ISA 673} Operating Systems Security
\end{itemize}

\item Information Systems (INFS)
\begin{itemize}
    \item \href{https://catalog.gmu.edu/search/?P=INFS%20740}{INFS} 740 Database Programming for the World Wide Web
\end{itemize}

\item Operations Research (OR)
\begin{itemize}
    \item \href{https://catalog.gmu.edu/search/?P=OR%20542}{OR 542} Operations Research: Stochastic Models
\end{itemize}
